---
title: "p8105_hw1_jx2371"
author: "Jingyu Xu"
date: "2018/9/21"
output: github_document
---
I set a globle option which hides the message and warning information.
```{r setup}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```
# Problem 1
## create a data frame
Firstly, a code chunk is created to create a data frame comprised of:  
1)A random sample of size 10 from a uniform[0, 5] distribution  
2)A logical vector indicating whether elements of the sample are greater than 2  
3)A (length-10) character vector  
4)A (length-10) factor vector
```{r create_dataframe_1}
library(tidyverse)
df_1 = tibble(
vec_rnorm = rnorm(10, mean=0, sd=5),
vec_logical = c(vec_rnorm>2), 
vec_character = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
vec_factor = factor(c("male", "male", "female", "female", "male", "male", "female", "female", "male", "female"))
 )
```

## caculate the mean
Then, a code chunck is created to caculate the mean of each variables in the dataframe(df_1)
```{r caculate_mean_df1}
mean(df_1$vec_rnorm)
mean(df_1$vec_logical)
mean(df_1$vec_character)
mean(df_1$vec_factor)
```

From the output, the mean of numeric and logical variables can be caculated, while those of the character and factor ones return to NA.  

## convert the variables
And I write a code chunk that applies the as.numeric function to the logical, character, and factor variables. specially，the output is hided.
```{r convert_numeric, results='hide'}
as.numeric(df_1$vec_logical)
as.numeric(df_1$vec_character)
as.numeric(df_1$vec_factor)
```
As for the logical variables, "TRUE" is converted to "1" and "FALSE" is converted to "0". And the character variables are converted to NA. The factor variables are converted to "1" and "2".  

Then, convert the character variable from character to factor to numeric.
```{r convert_factor_numeric, results='hide'}
as.numeric(as.factor(df_1$vec_character))
```
We can see the 10 different factor variables are converted to continous integers from 1 to 10.

Last, convert the factor variable from factor to character to numeric.
```{r convert_character_numeric, results='hide'}
as.numeric(as.character(df_1$vec_factor))
```
We can see the factor variables are finally converted to NA.


